\bf What is the Best Way to Display Two Time Series to Read Association?

### 2016-02-01 paper/paper.Rnw
Citations

Further analysis was carried out using \citet{R} version 3.1.2 and \citet{Rstudio} version 0.99.484 using the packages: \citet{dplyr}, \citet{ggplot2}, \citet{grid}, \citet{gridExtra}, \citet{gridSVG}, \citet{knitr}, \citet{maps}, \citet{mFilter}, \citet{mnormt}, \citet{nullabor}, \citet{stringr} and \citet{tidyr}.

>>>>

Further analysis was carried out using \citet{R} version 3.1.2 and \citet{Rstudio} version 0.99.484 using the packages: dplyr, ggplot2, grid, gridExtra, gridSVG, knitr, maps, mFilter, mnormt, nullabor, string and tidyr.
%\citet{dplyr}, \citet{ggplot2}, \citet{grid}, \citet{gridExtra}, \citet{gridSVG}, \citet{knitr}, \citet{maps}, \citet{mFilter}, \citet{mnormt}, \citet{nullabor}, \citet{stringr} and \citet{tidyr}.
